Sparse Word Embeddings for Multi-domain Machine Translation

### 2019-05-13 2019/emnlp/sparse.tex
add
new

then optimize each $\theta_i$ (as additional factor used for fine-tuning the model to the domain $D(C_{i})$) the perplexity with respect to true distribution of domain
\begin{equation}
\theta^*_{i} = \displaystyle{\mathop{\argmin}_{\theta_i}}E_{(x,y) \sim D(C_{i})}[-log(p_{\theta_i,\theta^*_s}(y|x,i))]
\end{equation} 
Our first approach to multi-domain machine translation is to build such trivial solution in calibrating positions and sizes of domain paramters $\theta_i$ and shared parameters $\theta_s$ inside one architecture.
\subsection{Sparse word embedding}
\label{sec:sparse}
This section explains a new design for word embedding used in multi-domain model. As mentioned above, we separate parameter set into $D+1$ parameter sets correspond to D domains and one shared paramater set. Our first attempt is to split standard vector word embedding into $D+1$ regions named $\theta_i$ for $i \in [1,..,D]$ and $\theta_s$.
\begin{figure}[h]
\center
    \includegraphics[width=0.8\linewidth]{Sparse1}
    \caption{Sparse word embeddings. The red region contains units that are activated only when an input from the corresponding domain is presented; the other (green) regions are deactivated; the blue (generic) region is always activated.} 
    \label{fig:network}
  \end{figure}
\fyTodo{Explain vanishing ?}
Figure~\ref{fig:network} presents our proposed design. During backprogation, the \fyTodo{fix notation}{projection matrix $P$} receives vanishing gradient at regions corresponding to deactivated regions in the word embedding. Those regions are also vanished in forward step, thus do not interfere the training on the domain to which they do not correspond.

Denote
$p_{t} = P * w_{t} = P_g \omega_g(t) + \displaystyle{\mathop{\sum}_{i \in [1,..,d]} P_i * \omega_i(t)}$\\
where $w_{t}$ is word embedding of token $x_{t}$  is projection of word embedding (Transformer \cite{Vaswani17attention}, recurrent \cite{bahdanau2014neural})
Assume $x_{t}$ belongs to domain $i$, thus $w_j(t) = 0 \forall j \neq i$. Denote $P_j$ the rows of the projection matrix $P$ corresponding to the deactivated region $w_j$.
\begin{equation}
\begin{split}
\frac{\partial L(y_t,x_t)}{\partial P_j} &=\frac{\partial L}{\partial p}(p_t) * \frac{\partial p_t}{\partial P_j} \\
								&= \frac{\partial L}{\partial p}(p_t) * w_j(t)\\
									&=0
\end{split} 
\forall j \neq i
\end{equation}
\subsection{Implementation Details}
The complex structure of State-of-the-art architecture Transformer \cite{Vaswani17attention} and popular recurrent network \cite{bahdanau2014neural} makes the implementation of sparse embedding non-obvious. Indeed, Transformer involve positional embedding and residual connections which are not homogeneous for domain-regions. Therefore, in our first implementation, we used an dense layer to fuse domain-region and generic region before applying positional embedding and residual connection. This implementation limits the finetuning effect at only word level.\\
Furthermore, because word embeddings are involved in three parts of standard encoder-decoder structure, which are input of encoder, input of decoder and projection before softmax, we have 7 possibilities to apply sparse embedding. However, due to high memory cost, we only want to apply sparse embedding on the source side. \fyTodo{Explain this. Future work ?}

@@

To reduce size of vocabulary, we apply Byte-Pair Encoding with 30000 merge operations, then select approximately 30000 frequent words to build vocabulary for each language. 

@@

To validate our findings, we compared sparse embedding model with standard models using State-of-the-Art Transformer \cite{Vaswani17attention} architecture and Attention Recurrent Neural Network architecture. Our baselines consist of generic models trained with mixed corpora (denoted mixed in the table of scores); models finetuned to each domain using 15000 iterations over in-domain data (denoted $+ft_{EMEA}$, $+ft_{EPPS}$, $+ft_{ECB}$ in the table of scores); models using Domain features of \cite{Kobus17domaincontrol} (noted DC in the table of scores) and multi-domain model proposed by \cite{Zeng18multidomain} (denoted WDCMT in the table of scores). \\

@@

@@

For the implementation of sparse embeddings, we split the vector embedding of size 512 into four regions with size $[8,8,8,488]$ for instance, the choice will be dicussed in \ref{secc:region_size}. If sentence comes from domain $i$, regions for domains $j,\forall j \neq i$ will be masked as 0 while generic region is always activated. We then use a dense layer of size 512 to fuse the active domain region and the generic region.

@@

Each iteration of algorithm \ref{algo:1}, the batch contains 2 types of word embedding for each sentence: using only generic region; using generic region and present domain region. The reason to do this is to minimize simultaneously both losses: \\
$\theta^*_{s}=\displaystyle{\mathop{\argmin}_{\theta_s}}E_{(x,y) \sim D(\displaystyle{\mathop{\cup}_{i \in [1,..,d]}}C_{i})}[-log(p_{\theta_s}(y|x))]$ \\ 
$ \theta^*_{i}=\displaystyle{\mathop{\argmin}_{\theta_i}}E_{(x,y) \sim D(C_{i})}[-log(p_{\theta_i,\theta^*_s}(y|x,i))]
$ 
We admit that this is not the optimal way. However, this procedure makes training very simple. \fyTodo{Explain technicalities - future work ?}

@@

\subsection{Results}
\begin{table*}
\begin{center}
 \begin{tabularx}{\textwidth}{|| X | X | X | X | X | X | X | X | X ||} 
 \hline
 Models & EMEA test & EPPS test & ECB test & khresmoi (EMEA domain) & test 2007 (EPPS domain) & newstest 2009 & newstest 2014 & IWSLT test 2010 \\ [0.5ex] 
 \hline\hline
 Mixed & 67.69 & 37.5 & 53.49 & 34.86 & 30.96 & 20.98 & 28.56 & 25.7 \\
 \hline
 EMEA-finetuned & 76.77 & 17.16 & 11.99 & 29.58 & 14.25 & 9.92 & 11.64 & 11.10 \\
 \hline
 EPPS-finetuned & 20.86 & 37.04 & 24.53 & 31.86 & 30.97 & 20.72 &  & 11.1 \\
 \hline
 ECB-finetuned & 26.93 & 27.09 & 56.52 & 22.04 & 22.92 & 12.94 & 17.51 & 13.99 \\
 \hline
 Sparse(1) & 74.26 & 37.67 & 54.07 & 33.85 & 30.86 & 20.97 & 28.11 & 25.70 \\
 \hline
 Sparse(2) & 73.97 & 37.81 & 53.67 & 34.17 & 30.93 & 20.97 & 28.11 & 25.7 \\
 \hline
 Sparse(3) &  &  &  &  &  &  &  & \\
 \hline
 Domain Control & 67.87 & 37.31 & 54.14 & 33.63 & 31.09 &  & & \\
 \hline
\end{tabularx}
\end{center}

@@

\begin{table*}
\begin{center}
 \begin{tabularx}{\textwidth}{|| X | X | X | X | X | X | X | X | X ||} 
 \hline
 Models & EMEA test & EPPS test & ECB test & khresmoi (EMEA domain) & test 2007 (EPPS domain) & newstest 2009 & newstest 2014 & IWSLT test 2010 \\ [0.5ex] 
 \hline\hline
 Mixed & 64.57 & 26.47 & 68.67 & 21.77 & 23.50 & 13.9 & 17.04 & 18.85 \\
 \hline
 EMEA-finetuned & 68.35 & 17.02 & 32.87 & 21.15 & 15.94 & 8.92 & 11.21 & 13.49 \\
 \hline
 EPPS-finetuned & 36.19 & 26.29 & 40.71 & 19.67 & 23.69 & 14.08 & 16.47 & 19.24 \\
 \hline
 ECB-finetuned & 24.72 & 18.36 & 74.05 & 11.31 & 16.64 & 9.11 & 10.8 & 11.0 \\
 \hline
 Sparse(1) & 70.9 & 26.30 & 68.9 & 21.42 & 23.73 & 13.99 & 16.57 & 18.82 \\
 \hline
 Sparse(2) & 70.86 & 26.14 & 68.59 & 21.95 & 23.79 & 13.99 & 16.57 & 18.82 \\
 \hline
 Sparse (3) &  &  &  &  &  &  &  & \\
 \hline
 Domain Control & 63.48 & 26.27 & 66.95 & 21.45 & 23.95 & & & \\
 \hline
\end{tabularx}
\end{center}
\caption{BLEU score for Transformer in language pair English - German. Notations are same as Table~\ref{tab:1}}
\label{tab:2}
\end{table*}

\begin{table*}
\begin{center}
 \begin{tabularx}{\textwidth}{|| X | X | X | X | X | X | X | X | X ||} 
 \hline
 Models & EMEA test & EPPS test & ECB test & khresmoi (EMEA domain) & test 2007 (EPPS domain) & newstest 2009 & newstest 2014 & IWSLT test 2010 \\ [0.5ex] 
 \hline\hline
 Mixed & 65.42 & 34.7 & 51.38 & 29.27 & 28.95 & 17.82 & 22.21 & 21.63 \\
 \hline
 EMEA-finetuned  & 72.06 & 18.62 & 16.78 & 25.88 & 13.38 & 9.26 & 10.94 & 5.73 \\
 \hline
 EPPS-finetuned & 35.47 & 34.61 & 39.56 & 27.11 & 28.8 & 17.3 & 21.85 & 20.61 \\
 \hline
 ECB-finetuned & 21.93 & 22.6 & 51.53 & 14.74 & 20.23 & 9.74 & 12.10 & 10.47 \\
 \hline
 Sparse (1) & 71.73 & 35.21 & 50.91 & 29.62 & 29.05 & 17.92 & 23.00 & 20.96 \\
 \hline
 Sparse (2) & 70.59 & 35.22 & 49.68 & 29.51 & 29.32 & 17.92 & 23.00 & 20.96 \\
 \hline
 Sparse (3) &  &  &  &  &  &  &  & \\
 \hline
 Domain Control & 68.26 & 35.13 & 50.09 & 27.86 & 29.34 & & & \\
 \hline
 WDCMT (conditional GRU) & 68.76 & 35.71 & 52.75 & 32.03 & 29.81 & 19.58 & 24.63 & 23.28 \\
 \hline 
\end{tabularx}
\end{center}
\caption{bpe-detokenized BLEU score for Recurrent network architecture on language pair English-French. Notations as same as figure \ref{tab:1} except that other models from WDCMT of \cite{Zeng18multidomain} use Bidirectional-LSTM}
\label{tab:3}
\end{table*}

\begin{table*}
\begin{center}
 \begin{tabularx}{\textwidth}{|| X | X | X | X | X | X | X | X | X ||} 
 \hline
 Models & EMEA test & EPPS test & ECB test & khresmoi (EMEA domain) & test 2007 (EPPS domain) & newstest 2009 & newstest 2014 & IWSLT test 2010 \\ [0.5ex] 
 \hline\hline
 Mixed & 57.37 & 23.1 & 63.54 & 17.39 & 20.65 & 10.69 & 11.51 & 14.29 \\
 \hline
 EMEA-finetuned & 65.64 & 12.36 & 15.93 & 15.38 & 11.1 & 5.54 & 6.22 & 7.6 \\
 \hline
 EPPS-finetuned & 24.9 & 22.98 & 26.26 & 13.55 & 20.95 & 10.58 & 11.33 & 14.32 \\
 \hline
 ECB-finetuned & & & & & & & & \\
 \hline
 Sparse (1) & 63.43 & 22.66 & 64.4 & 16.99 & 20.63 & 10.89 & 11.45 & 14.26 \\
 \hline
 Sparse (2) & 63.27 & 22.62 & 63.7 & 17.26 & 20.69 & 10.89 & 11.45 & 14.26 \\
 \hline
 Sparse (3) &  &  &  &  &  &  &  & \\
 \hline
 Domain Control & 62.53 & 23.74 & 65.71 & 16.88 & 21.85 & & & \\
 \hline
 WDCMT (conditional GRU) & & & & & & & & \\
 \hline 
\end{tabularx}
\end{center}
\caption{BLEU score for Recurrent network on language pair English - German. The notation is same as figure \ref{tab:3}}
\label{tab:4}
\end{table*}

\section{Discussion\label{sec:Discussion}}
\subsection{Region's size \label{secc:region_size}}
\subsection{Word embedding analysis}

>>>>

then optimize each $\theta_i$ (as additional factor used for fine-tuning the model to the domain $D(C_{i})$) the perplexity with respect to true distribution of domain
\begin{equation}
\theta^*_{i} = \displaystyle{\mathop{\argmin}_{\theta_i}}E_{(x,y) \sim D(C_{i})}[-log(p_{\theta_i,\theta^*_s}(y|x,i))]
\end{equation} 
Our first approach to multi-domain machine translation is to build such trivial solution by assigning different regions of word embedding vector to set of domain paramters $\theta_i$ and set of shared parameters $\theta_s$ while keep sharing other parameters between domains.
\subsection{Sparse word embedding}
\label{sec:sparse}
This section explains a new design for word embedding used in multi-domain model. As mentioned above, we separate parameter set into $D+1$ parameter sets correspond to D domains and one shared paramater set. Our first attempt is to split standard vector word embedding into $D+1$ regions named $\theta_i$ for $i \in [1,..,D]$ and $\theta_s$.
\begin{figure}[h]
\center
    \includegraphics[width=0.8\linewidth]{Sparse1}
    \caption{Sparse word embeddings. The red region contains units that are activated only when an input from the corresponding domain is presented; the other (green) regions are deactivated; the blue (generic) region is always activated.} 
    \label{fig:network}
  \end{figure}
\fyTodo{Explain vanishing ?}
Figure~\ref{fig:network} presents our proposed design. During backprogation, the \fyTodo{fix notation}{projection matrix $M$} receives gradient 0 at regions corresponding to deactivated regions in the word embedding. Those regions are also masked in forward step, thus do not interfere the training on the domain to which they are not assigned.

Let $\tilde{x}_{t} = M * e_{t} = M_g e_g(t) + \displaystyle{\mathop{\sum}_{i \in [1,..,d]} M_i * e_i(t)}$ be the projection of word embedding where $e_{t}$ is word embedding of token $x_{t}$, M is projection matrix, $M_j \forall j \in [1...d]$ is row block corresponding to domain region $j$ (Transformer \cite{Vaswani17attention}, recurrent \cite{bahdanau2014neural})\\
Assume the batch belongs to domain $i$, then $e_j(t) = 0$ $\forall j \neq i$,$\forall t$. 
\begin{equation}
\begin{split}
\frac{\partial L(x,y)}{\partial M_j} &= \sum_{t}\frac{\partial L}{\partial \tilde{x}_t}(x_t) * \frac{\partial \tilde{x}_t}{\partial M_j} \\
								&= \sum_{t} \frac{\partial L}{\partial \tilde{x}_t}(x_t) * e_j(t)\\
									&=0
\end{split} 
\forall j \neq i
\end{equation}

The complex structure of State-of-the-art architecture Transformer \cite{Vaswani17attention} and popular recurrent network \cite{bahdanau2014neural} makes the implementation of sparse embedding non-obvious. Indeed, Transformer involve positional embedding and residual connections which are not homogeneous for domain-regions. Therefore, in our first implementation, we used an dense layer to fuse domain-region and generic region before applying positional embedding and residual connection. This implementation limits the finetuning effect at only word level.\\
Furthermore, because word embeddings are involved in three parts of standard encoder-decoder structure, which are input of encoder, input of decoder and projection before softmax, we have 7 possibilities to apply sparse embedding. However, due to high memory cost, we only want to apply sparse embedding on the source side. \fyTodo{Explain this. Future work ?}

@@

To reduce size of vocabulary, we apply Byte-Pair Encoding with 30000 merge operations, then select approximately 30000 the most frequent words to build vocabulary for each language. 

@@

To validate our findings, we compared sparse embedding model with standard models using State-of-the-Art Transformer \cite{Vaswani17attention} architecture and Attention Recurrent Neural Network architecture. Our baselines consist of generic models trained with mixed corpora (denoted mixed in the table of scores); models finetuned to each domain using (10000, 15000, 5000) iterations over in-domain data (denoted $+ft_{EMEA}$, $+ft_{EPPS}$, $+ft_{ECB}$ in the table of scores); models using Domain features of \cite{Kobus17domaincontrol} (noted DC in the table of scores) and multi-domain model proposed by \cite{Zeng18multidomain} (denoted WDCMT in the table of scores). \\

@@

To train NMT systems, we use Adam($\beta_1=0.9$, $\beta_2 = 0.999$, $\alpha=0.0005$) for Attention Recurrent Neural Network; and Adam with $\beta_1=0.9$, $\beta_2= 0.98$, with Noam decay \cite{Vaswani17attention} ($warmup\_steps=4000$) for Transformer.

@@

For the implementation of sparse embeddings, we split the vector embedding of size 512 into four regions: 3 domain specific and 1 generic, with size $[8,8,8,488]$, the choice will be dicussed in \ref{secc:region_size}. If sentence comes from domain $i$, regions for domains $j \neq i$ will be masked as 0 while generic region is always activated. We then use a dense layer of size 512 to fuse the active domain region and the generic region.

@@

In the training, we use same optimization algorithm as the baselines.
Each iteration of algorithm \ref{algo:1}, we use 2 batches: generic batch using only generic region; and domain batch using generic region and domain region. The reason to do that is to minimize simultaneously both losses: \\
$\theta^*_{s}=\displaystyle{\mathop{\argmin}_{\theta_s}}E_{(x,y) \sim D(\displaystyle{\mathop{\cup}_{i \in [1,..,d]}}C_{i})}[-log(p_{\theta_s}(y|x))]$ \\ 
$ \theta^*_{i}=\displaystyle{\mathop{\argmin}_{\theta_i}}E_{(x,y) \sim D(C_{i})}[-log(p_{\theta_i,\theta^*_s}(y|x,i))]
$

@@

\subsection{Results}
\begin{table*}
\begin{center}
 \begin{tabularx}{\textwidth}{|| X | X | X | X | X | X | X | X | X ||} 
 \hline
 Models & EMEA test & EPPS test & ECB test & khresmoi (EMEA domain) & test 2007 (EPPS domain) & newstest 2009 & newstest 2014 & IWSLT test 2010 \\ [0.5ex] 
 \hline\hline
 Mixed & 67.69 & 37.5 & 53.49 & 34.86 & 30.96 & 20.98 & 28.56 & 25.7 \\
 \hline
 EMEA-finetuned & 76.77 & 17.16 & 11.99 & 29.58 & 14.25 & 9.92 & 11.64 & 11.1 \\
 \hline
 EPPS-finetuned & 20.86 & 37.04 & 24.53 & 31.86 & 30.97 & 20.72 & 28.33 & 11.1 \\
 \hline
 ECB-finetuned & 26.93 & 27.09 & 56.52 & 22.04 & 22.92 & 12.94 & 17.51 & 13.99 \\
 \hline
 Sparse(1) & 74.26 & 37.67 & 54.07 & 33.85 & 30.86 & 20.97 & 28.11 & 25.7 \\
 \hline
 Sparse(2) & 73.97 & 37.81 & 53.67 & 34.17 & 30.93 & 20.97 & 28.11 & 25.7 \\
 \hline
 Sparse(3) &  &  &  &  &  &  &  & \\
 \hline
 Domain Control & 67.87 & 37.31 & 54.14 & 33.63 & 31.09 &  20.1 & 26.52 & 24.81\\
 \hline
\end{tabularx}
\end{center}

@@

\begin{table*}
\begin{center}
 \begin{tabularx}{\textwidth}{|| X | X | X | X | X | X | X | X | X ||} 
 \hline
 Models & EMEA test & EPPS test & ECB test & khresmoi (EMEA domain) & test 2007 (EPPS domain) & newstest 2009 & newstest 2014 & IWSLT test 2010 \\ [0.5ex] 
 \hline\hline
 Mixed & 64.57 & 26.47 & 68.67 & 21.77 & 23.50 & 13.9 & 17.04 & 18.85 \\
 \hline
 EMEA-finetuned & 68.35 & 17.02 & 32.87 & 21.15 & 15.94 & 8.92 & 11.21 & 13.49 \\
 \hline
 EPPS-finetuned & 36.19 & 26.29 & 40.71 & 19.67 & 23.69 & 14.08 & 16.47 & 19.24 \\
 \hline
 ECB-finetuned & 24.72 & 18.36 & 74.05 & 11.31 & 16.64 & 9.11 & 10.8 & 11.0 \\
 \hline
 Sparse(1) & 70.9 & 26.30 & 68.9 & 21.42 & 23.73 & 13.99 & 16.57 & 18.82 \\
 \hline
 Sparse(2) & 70.86 & 26.14 & 68.59 & 21.95 & 23.79 & 13.99 & 16.57 & 18.82 \\
 \hline
 Sparse (3) &  &  &  &  &  &  &  & \\
 \hline
 Domain Control & 63.48 & 26.27 & 66.95 & 21.45 & 23.95 & 13.94 & 16.45 & 18.78  \\
 \hline
\end{tabularx}
\end{center}
\caption{BLEU score for Transformer in language pair English - German. Notations are same as Table~\ref{tab:1}}
\label{tab:2}
\end{table*}

\begin{table*}
\begin{center}
 \begin{tabularx}{\textwidth}{|| X | X | X | X | X | X | X | X | X ||} 
 \hline
 Models & EMEA test & EPPS test & ECB test & khresmoi (EMEA domain) & test 2007 (EPPS domain) & newstest 2009 & newstest 2014 & IWSLT test 2010 \\ [0.5ex] 
 \hline\hline
 Mixed & 65.42 & 34.7 & 51.38 & 29.27 & 28.95 & 17.82 & 22.21 & 21.63 \\
 \hline
 EMEA-finetuned  & 72.06 & 18.62 & 16.78 & 25.88 & 13.38 & 9.26 & 10.94 & 5.73 \\
 \hline
 EPPS-finetuned & 35.47 & 34.61 & 39.56 & 27.11 & 28.8 & 17.3 & 21.85 & 20.61 \\
 \hline
 ECB-finetuned & 21.93 & 22.6 & 51.53 & 14.74 & 20.23 & 9.74 & 12.10 & 10.47 \\
 \hline
 Sparse (1) & 71.73 & 35.21 & 50.91 & 29.62 & 29.05 & 17.92 & 23.00 & 20.96 \\
 \hline
 Sparse (2) & 70.59 & 35.22 & 49.68 & 29.51 & 29.32 & 17.92 & 23.00 & 20.96 \\
 \hline
 Sparse (3) &  &  &  &  &  &  &  & \\
 \hline
 Domain Control & 68.26 & 35.13 & 50.09 & 27.86 & 29.34 & 16.25 & 20.95 & 21.16 \\
 \hline
 WDCMT (conditional GRU) & 68.76 & 35.71 & 52.75 & 32.03 & 29.81 & 19.58 & 24.63 & 23.28 \\
 \hline 
\end{tabularx}
\end{center}
\caption{bpe-detokenized BLEU score for Recurrent network architecture on language pair English-French. Notations as same as figure \ref{tab:1} except that other models from WDCMT of \cite{Zeng18multidomain} use Bidirectional-LSTM}
\label{tab:3}
\end{table*}

\begin{table*}
\begin{center}
 \begin{tabularx}{\textwidth}{|| X | X | X | X | X | X | X | X | X ||} 
 \hline
 Models & EMEA test & EPPS test & ECB test & khresmoi (EMEA domain) & test 2007 (EPPS domain) & newstest 2009 & newstest 2014 & IWSLT test 2010 \\ [0.5ex] 
 \hline\hline
 Mixed & 57.37 & 23.1 & 63.54 & 17.39 & 20.65 & 10.69 & 11.51 & 14.29 \\
 \hline
 EMEA-finetuned & 65.64 & 12.36 & 15.93 & 15.38 & 11.1 & 5.54 & 6.22 & 7.6 \\
 \hline
 EPPS-finetuned & 24.9 & 22.98 & 26.26 & 13.55 & 20.95 & 10.58 & 11.33 & 14.32 \\
 \hline
 ECB-finetuned & 41.8 & 15.97 & 71.07 & 10.77 & 14.67 & 7.06 & 7.66 & 8.07 \\
 \hline
 Sparse (1) & 63.43 & 22.66 & 64.4 & 16.99 & 20.63 & 10.89 & 11.45 & 14.26 \\
 \hline
 Sparse (2) & 63.27 & 22.62 & 63.7 & 17.26 & 20.69 & 10.89 & 11.45 & 14.26 \\
 \hline
 Sparse (3) &  &  &  &  &  &  &  & \\
 \hline
 Domain Control & 62.53 & 23.74 & 65.71 & 16.88 & 21.85 & 9.24 & 11.15 & 14.97 \\
 \hline
 WDCMT (conditional GRU) & 64.05 & 22.82 & 67 & 15.94 & 20.57 & 10.15 & 11.45 & 13.66 \\
 \hline 
\end{tabularx}
\end{center}
\caption{BLEU score for Recurrent network on language pair English - German. The notation is same as figure \ref{tab:3}}
\label{tab:4}
\end{table*}

\section{Discussion\label{sec:Discussion}}
\subsection{Sparse's performance}
The 4 table show remarquable improvement in EMEA translation which is comparable with finetuned model. Sparse model 
\subsection{Region's size \label{secc:region_size}}
\subsection{Word embedding analysis}
